Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
be consistent in spelling \ell_1
Also turned off hyperref as it consistently breaks stuff.
duplicate citations

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}

@@

From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the NumPy and
SciPy \citep{vanderwalt2011, varoquaux2013scipy} libraries.
Of these, NumPy augments Python with a numeric array datatype
and associated array computing primitives \citep{vanderwalt2011},
while SciPy extends it further
by making common numeric operations available,
either by implementing those in Python/NumPy,
or by wrapping existing C/C{}\verb!++!/Fortran implementations.
In a similar vein, \sklearn extends the general-purpose language Python
with a set of composable machine learning operations.

@@

\begin{align*}
         & \textsf{stopwords} \in \{0, 1\}                      \\
  \times & \; \textsf{tf} \in \{\textsf{linear}, \textsf{log}\} \\
  \times & \; n_\textsf{features} \in \{1000, 2000, 5000\}      \\
  \times & \; \textsf{norm} \in \{L_1, L_2\}                    \\
  \times & \; C \in \{10, 100, 1000\}
\end{align*}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
%\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}

@@

From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the NumPy and SciPy libraries.
Of these, NumPy \citep{vanderwalt2011} augments Python
with a numeric array datatype and associated array computing primitives,
while SciPy \citep{varoquaux2013scipy} extends it further
by making common numeric operations available,
either by implementing those in Python/NumPy,
or by wrapping existing C/C{}\verb!++!/Fortran implementations.
In a similar vein, \sklearn extends the general-purpose language Python
with a set of composable machine learning operations.

@@

\begin{align*}
         & \textsf{stopwords} \in \{0, 1\}                      \\
  \times & \; \textsf{tf} \in \{\textsf{linear}, \textsf{log}\} \\
  \times & \; n_\textsf{features} \in \{1000, 2000, 5000\}      \\
  \times & \; \textsf{norm} \in \{\ell_1, \ell_2\}              \\
  \times & \; C \in \{10, 100, 1000\}
\end{align*}
